The Tor Network - Design and Defenses \\ \Large Computer Security 1 - CS5460 \\ \LaTeX{}

### 2013-12-06 paper.tex
conclusion expansion

In 2011, Zhen Ling \textit{et al} described an active watermark attack in which an attacker operates a reverse proxy and actively manipulates the size of the TCP packets transmitted to the exit node. Simultaneously, the attacker also runs a recovery method to detect the watermark on the user side. His watermark was a short sequence of 1s and 0s that could be encoded into the packet patterns. To transmit a 0, the attacker sends 498 bytes worth of web traffic to the Tor exit node, which is the exact size of the data portion of a Tor cell. Combined with the cell headers, the data packs into a single Tor cell of 512 bytes. To transmit a 1, the attacker sends 2444 bytes of data to the exit. The standard Maximum Transmission Unit (MTU) for Ethernet v2 lines is 1500 bytes and the TCP and IP headers are 20 and 32 bytes respectively, which means that a TCP packet can carry at most 1448 bytes of data. As the 2444 bytes from the attacker exceeds the MTU, two TCP packets are needed, one with a 1448-byte payload and the other with a 996-byte payload. The first TCP packet is received by the relay and is packed into three equally-sized cells, with padding added to the 452 bytes of the third cell. The second TCP packet becomes two cells of 498 bytes each, and thus the 2444 bytes becomes five Tor cells. Then these cells are processed, encoded as TCP packets, and retransmitted to the next relay. However, due to the design of cell queuing algorithms, TCP retransmission, and MTU restrictions, the two TCP packets may be split and combined into Tor cells in up to five different ways, each leaving a discernible packet signature. The attacker can then monitor the traffic near the client, examining the packet patterns generated by the attack. If the embedded signal is found, then it is quite likely that the traffic flows are correlated. In their tests, Zhen Ling \textit{et al} achieved a detection rate of nearly 90\%, with a false positive rate of less than 4\%, concluding that such an attack could degrade anonymity.\cite{Ling2011}

@@

(obviously I need this. Summarize design, attacks, defenses, analysis, reviews in the literature, and then provide my opinion about the future)

>>>>

In 2011, Zhen Ling \textit{et al} described an active watermark attack in which an attacker operates a reverse proxy and actively manipulates the size of the TCP packets transmitted to the exit node. Simultaneously, the attacker also runs a recovery method to detect the watermark on the user side. His watermark was a short sequence of 1s and 0s that could be encoded into the packet patterns. To transmit a 0, the attacker sends 498 bytes worth of web traffic to the Tor exit node, which is the exact size of the data portion of a Tor cell. Combined with the cell headers, the data packs into a single Tor cell of 512 bytes. To transmit a 1, the attacker sends 2444 bytes of data to the exit. The standard Maximum Transmission Unit (MTU) for Ethernet v2 lines is 1500 bytes and the TCP and IP headers are 20 and 32 bytes respectively, which means that a TCP packet can carry at most 1448 bytes of data. As the 2444 bytes from the attacker exceeds the MTU, two TCP packets are needed, one with a 1448-byte payload and the other with a 996-byte payload. The first TCP packet is received by the relay and is packed into three equally-sized cells, with padding added to the 452 bytes of the third cell. The second TCP packet becomes two cells of 498 bytes each, and thus the 2444 bytes becomes five Tor cells. Then these cells are processed, encoded as TCP packets, and retransmitted to the next relay. However, due to the design of cell queuing algorithms, TCP retransmission, and MTU restrictions, the two TCP packets may be split and combined into Tor cells in up to five different ways, each leaving a discernible packet signature. The attacker can then monitor the traffic near the client, examining the packet patterns generated by the attack. If the embedded signal is found, then it is quite likely that the traffic flows are correlated. In their tests, Zhen Ling \textit{et al} achieved a detection rate of nearly 90\%, with a false positive rate of less than 4\%, concluding that such an attack could degrade anonymity if applied in practice.\cite{Ling2011}

@@

Tor provides an anonymity and privacy layer by relaying end-user traffic through a circuit consisting of three randomized relays around the world. Traffic is encrypted with the session keys of each relay and then decrypted in an onion-like fashion as it passes through the circuit. No single relay knows both the source IP and its destination, so even single compromised relays are unable to correlate end users with their activities. This makes Tor much more resilient to adversaries than proxies or VPNs. For this reason, it is one of the most popular and secure tools to use against network surveillance, traffic analysis, and Internet censorship. Tor has been attacked by various organizations, agencies, and governments in an attempt to watch users, root out their identities, or restrict their access to information. Although its main adversaries are well-resourced, Tor's routing and cryptography protocols have made it very difficult for outsiders to penetrate its defenses.

However, Tor is not impenetrable. By far the most significant threat to Internet anonymity is carelessness: a user may publish enough electronic clues that point to their real-life identity. By design, Tor cannot defend against this. The most effective attacks against Tor itself have used exploits in the Tor Browser Bundle, Javascript, or the host operating system. These indirect attacks have been used in the past to successfully de-anonymize a few of its users. In other cases, traditional detective work has been used to take down hidden services inside the Tor network. However, in general the Tor routing protocol has proven fairly secure, with only a handful of theoretical attacks published and tested by researchers in the field. As Tor's documentation suggests, it is not a foolproof solution for online anonymity, and users must still be careful with their information.

Tor's developers and the open-source community continue to update the software with improved cryptography and preemptive security patches. This makes exploiting Tor a continual and difficult race against global open-source development, certainly a challenge for even well-resource adversaries. Indeed, an NSA appraisal released by the Guardian in October 2013 characterizes Tor as ``still the king of high secure, low latency Internet anonymity'' and that ``there are no contenders for the throne in waiting''. Tor's future looks bright.
